BERT Model Compression and Weight Sharing

### 2019-05-13 paper/paper.tex
Minor paper fix

\begin{abstract}
% \raggedright
  We apply model compression techniques to fine-tuned BERT on multiclass
  classification problems.  Knowledge distillation and DeepTwist-based compression techniques give
  us moderate compression benefits for a commensurate decrease in model
  performance. We achieve our most compelling results from employing the DeepTwist
  framework to share weights across BERT models fine-tuned for different tasks. Our work demonstrates most weights need not change in the fine-tuning
  process.
%   \item This document describes the expected style, structure, and rough
%   proportions for your final project write-up.
%   \item While you are free to break from this structure, consider it a strong
%   prior for our expectations of the final report.
%   \item Length is a hard constraint. You are only allowed max \textbf{8 pages}
%   in this format. While you can include supplementary material, it will not be
%   factored into the grading process. It is your responsibility to convey the
%   main contributions of the work in the length given.
  % \end{itemize}

@@

Deep Neural Networks (DNNs) have become the state-of-art for many tasks in
language modeling. At the same time, they have become progressively larger in
size, due to both larger out-of-box pretrained embeddings and deeper
networks. However, in order to deploy the models on more resource-constrained
devices, such as mobile devices or even older personal laptops, as opposed to
on cloud virtual machines, it is crucial to reduce the size of the models.

@@

In this paper, we demonstrate that the DeepTwist framework
\citep{lee2018deeptwist} is applicable to compressing fine-tuned BERT
\citep{devlin2018bert} on multiclass classification problems in addition to
computer vision tasks, though the drop in performance is less negligible.
Knowledge distillation also achieves the compression objective with more than
desired decrease in predictive accuracy.

@@

The most important contribution of this paper is that we proposed a new
weight-sharing method called ``Difference Pruning'' which imposes constraint on
the sparcity of weight difference with the pretrained BERT model. While
uncompressed fine-tuned BERT model achieves 92.9\% validation accuracy on
SST-2, the Difference Pruning model that keeps 99\% of the pretrained BERT
weights achieves 91.3\% on the validation set. This enables multiple language
modeling tasks to share the weights of pretrained BERT and each incurs minimal
extra storage space requirements.

@@

DNNs have become extremely large in size with growing complexities. A good
example is BERT \citep{devlin2018bert}, which represents a growing
literature in natural language processing in favor of pretraining 
\citep{peters2018deep,radford2018improving,radford2019language}, which
uses large models to learn from a large corpus of text in an unsupervised
manner. The goal of such pretraining is creating contextualized
representation of text in $\R^n$ which preserve certain structure of
language. For different tasks, the researcher then \emph{fine-tunes} the
pretrained model to the task, which may reach good performance since the
pretrained representations are well-behaved representations of language
strucutre. A downside of this framework is that each fine-tuned task
requires a unique set of weights, which, when coupled with the raw size of
these models, are cumbersome objects especially in a low hardware resource
environment.

The smaller \texttt{BERT-base-uncased} model has 110M parameters and takes
438 MB disk space to store. This
makes it very hard to deploy those models on mobile devices, which in most
cases have limited storage and RAM and low computational resources. As a
result, we are not able to store multiple models for different tasks on mobile
devices. Allocating hundreds of megabytes to to those models is also not
realistic for mobile apps such as Gmail or Facebook. And due to increasing
privacy concerns, users prefer models generating predictions based on their
input to be running locally instead of sending information to the cloud. Last
but not least, evaluating enormous models takes too much time on mobile
devices and can drain batteries significantly.

The challenge that we are facing is therefore how to compress DNNs in size
while keeping their predictive performance competitive with full model. We are interested in compressing the language representation model BERT.  It is the state-of-art result in many natural
language processing tasks  such as natural language inference, paraphrasing
and named entity recognition.

@@

There is a rich literature on compressing deep learning models, a selection
of which we review in this section. For a comprehensive review, see  
\citep{cheng2017survey}. The early work in compression is usually in a
multi-stage framework, where model is trained, compressed, and then
the compressed model is retrained for good performance.

\citet{han2015deep} applies compression techniques to computer vision,
where convolutional neural networks are popular and are often
overparameterized \citep{yang2019fsnet},
where the network is gradually \emph{pruned} and retrained in the first
stage, where small
weights are set
to zero and gradient connections severed. In the second stage, the weights
that survived pruning are clustered, and each cluster behaves like a single
weight, with identical gradients. In the last stage, the model is Huffman
encoded. Numerical experiments by \citet{han2015deep} show that the
compression does not seem to influence performance. Moreover, the benefits
of various compression techniques appear to stack without much loss in
compression benefit. Moreover, convolutional network sizes are dominated by
the convolution operations in
lower layers \citep{denton2014exploiting}. \citet{denton2014exploiting}
uses matrix factorization techniques on the matrices in convolutional
layers, which has low effective rank.

Pruning, quantization, and rank reduction are operations applied to a
particular network's weights without altering the network architecture. 
A different framework, knowledge distillation, first proposed by 
\citep{bucilua2006model} as
``knowledge transfer,'' was recently popularized by
\citep{hinton2015distilling}. In knowledge distillation, a simple network,
called the \emph{student network}, is not trained on the actual data but on
the output of the large network one wishes to compress, called the 
\emph{teacher network}. This procedure can even be extended by inserting
various
intermediate-sized networks between the teacher and student, intuitively
termed
\emph{teacher-assistant networks} \citep{mirzadeh2019improved}. We dicuss
knowledge distillation in detail in \Cref{sec:training}.

Compression techniques like pruning, quantization, and rank reduction can
also be incorporated into an end-to-end framework, known as 
\emph{DeepTwist}  \citep{lee2018deeptwist}, where training needs not be
interrupted in some multi-stage process. Under this
framework, the model parameters are occasionally distorted during training
time instead of only at the end. This framework has the benefit of simplified
training procedure and faster convergence and reduced requirement for
hyperparameter tuning. Experiment on MNIST dataset with DeepTwist shows that
LeNet-5 and LeNet-300-100 models are able to retain predictive accuracy under
high compression rate.

@@

An additional benefit from knowledge distillation arises from BERT's
pre-training. Because BERT is pretrained on large amounts of unstructured
data, it contains a powerful language model which likely would be impossible
to learn from the specific task's data-set. To an extent, relevant features
from this language model are what make BERT so powerful once it's fine-tuned.
Training the student network on BERT's output thus allows some of this
``outside knowledge'' to percolate toward the student network.

@@

\subsection{DeepTwist}

@@

We list a few methods of parameterizing the distortion step. 
\paragraphdot{Pruning} Consider a parameter vector $\bvartheta$, let
  $t_p$ be the $p$-th quantile of the vector $\bvartheta$. Then \[
  \prune(\bvartheta; p) = \one(|\bvartheta| > t_p) \odot \bvartheta
  \]
  is the vector where values in $\bvartheta$ below in absolute magnitude $t_p$
  are zeroed.

@@

  Pruning is an out-of-the-box procedure that works with any models. However,
  as a price of the generality, pruning fails to be tailored to the nature of
  BERT being a pretrained model. Suppose the pretrained weights $\bphi_0 $
  capture certain structure of language, then dramatic distortions to
  $\bphi_0$ essentially discards the information, especially early in the
  training loop. We may partially remedy this issue by either using a dynamic
  pruning rate, where pruning rate is small early in the training loop or by
  using layer-specific pruning rates, with layers in $\bert$ having a lower
  pruning rate than layers in $G$.

@@

We distort via \[
\rankreduce(\bvartheta; r) = \tilde U \tilde \Sigma \tilde V^\top,
\]
where $\tilde U, \tilde \Sigma, \tilde V$ are conforming matrices such that the
smallest values on the spectrum $\Sigma$ is zeroed out, as well as corresponding
values in $U,V$. If we keep only the $r$ largest spectral values, then we store
$\tilde U \tilde \Sigma$, an $n\times r$ matrix, and $\tilde V$, an $m\times r$
matrix. Thus, instead of storing $2nm$ floats, we may store $r(n+m)$, achieving
a compression rate of \[
\rho = 1-\frac{r(n+m)}{2mn}.
\]
Note however, that storing matrices in this manner requires an additional
matrix multiplication in evaluation time, since we have to compute the product
$\tilde U \tilde \Sigma \tilde V$.

\section{Methods}
In this section, we briefly discuss our experimental setup. We mostly
work with
SST-2, a binary sentiment classification task in the GLUE multitask benchmark
framework \citep{wang2018glue}. We also validate the model's
performance with trial on the Quora Question Pair (QQP) task, which is a
binary classification task for whether two questions are equivalent. We
train with a maximum sequence length of 64 and batch size of 32 on the
NC-6 and NC-12 virtual machines on Microsoft Azure. We use the basic 
\texttt{BERT-base-uncased} model for our experimental results. We employ
early stopping in training, with patience of 1 epoch, and early stopping is
guided by validation loss.

@@

For knowledge distillation experiments, we use various configurations of the
student network: \paragraphdot{LSTM} We use a one-layer LSTM network with hidden
dimension $H=200$. We first embed the one-hot representation of tokens, and we
feed the embeddings through an LSTM. We then map the last hidden state of the
LSTM through a linear layer for classification.  \paragraphdot{CNN} We use an
implementation\footnote{\url{https://github.com/jfilter/cnn-text-classification-pytorch/blob/master/cnn_text_classification/model.py}}
of \citet{kim2014convolutional} with kernel sizes $(3,4,5)$, hidden size
$H=300$, no dropout and 50\% dropout, and $20$ kernels for each kernel
size.\footnote{These are default in the implementation we used.}

@@

We show our results in \Cref {tab:deeptwist_results,tab:kd_results}. In the top
pane of \Cref {tab:deeptwist_results}, we show the result of various
DeepTwist-based compression techniques on the sentiment classification task,
SST-2, stratifying by method and then by parameter of the method. Difference
pruning, pruning, and rank reduction are implemented as \emph{distortion by
layer} (see \Cref{sec:model}), where as \emph{difference pruning (global)}
indicates difference pruning, but pooling all parameter values from all layers.
The bottom pane of \Cref{tab:deeptwist_results} shows the performance on QQP of
some competitive-performing model setups on SST-2, which are all
difference-pruning based. In \Cref{tab:kd_results}, we present some knowledge
distillation experiments, with the student network being an LSTM or a CNN, with
or without dropout \citep{kim2014convolutional}.

Pruning admits a simple upper bound for compression, which is simply the
pruning ratio.\footnote{The exact compression rate is complicated, due to
the sparse data structure implemented for the compressed model} Compression
rate for difference pruning depends on the number of tasks the user
desires to perform, since difference pruning is understood to be a form of
weight sharing. In that context, the (upper bound) compression rate of
difference
pruning
is also self-evident. The compression rate achieved by rank reduction is \[
\rho = 1 - \frac{r(n+m)}{2mn}.
\]
Since most matrices in \texttt{BERT-base-uncased} is $768\times 768,$ the
compression rate is approximately \[
\rho \approx 1 - \frac{r}{768} = (74.0\%,
80.5\%,
87.0\%,
93.5\%)
\]
for $r = (200,150,100,50)$, respectively.

For the most part, difference pruning seems to be robust to the pruning
rate. As a sanity check, we include difference pruning with 100\% pruning
rate, which is equivalent to BERT model without fine-tuning, and obtaining
essentially uniform results on the validation set. Difference pruning also
seems to outperform both ``first-order'' DeepTwist techniques, pruning and
rank reduction, which is unsurprising as difference pruning uses more
parameters and uses parameters that are pretrained. Difference pruning also
seems to extend to other tasks in GLUE, as it retains its behavior in
SST-2 to QQP, for the most part. Knowledge distillation seems less
promising. While knowledge distillation
slightly improves upon the model directly trained on data, it does not
fully replicate the performance of the teacher network. We now discuss our
results in detail.

% \begin{itemize}
% \item What were the results comparing previous work / baseline systems / your
% systems on the main task?
% \item What were the secondary results comparing the variants of your system?
% \item This section should be fact based and relatively dry. What happened,
% what was significant?
% \end{itemize}

@@

% \begin{table}[tbh]
%         \caption{Results for DeepTwist}
%         \label{tab:deeptwist_results}
%         \centering
%         \vspace{1em}
%         \begin{tabular}{lccccc}
% \toprule
% {} &               type &  param &  val loss &   val acc \\
% {} & 
% \hypertarget{tabcol:1}{(1)} & \hypertarget{tabcol:2}{(2)} & \hypertarget{tabcol:3}{(3)} & \hypertarget{tabcol:4}{(4)} \\ \midrule
% 0  &  diff prune global &   $90$ &   $0.211$ &   $0.912$ \\
% 1  &              prune &   $20$ &   $0.291$ &   $0.886$ \\
% 2  &              prune &   $80$ &   $0.532$ &   $0.767$ \\
% 3  &         diff prune &   $80$ &   $0.222$ &   $0.916$ \\
% 4  &  diff prune global &   $99$ &       --- &       --- \\
% 5  &  diff prune global &   $90$ &   $0.213$ &   $0.916$ \\
% 6  &         diff prune &   $40$ &   $0.203$ &   $0.909$ \\
% 7  &                rank reduction &   $50$ &   $0.490$ &   $0.810$ \\
% 8  &                rank reduction &  $200$ &   $0.459$ &   $0.845$ \\
% 9  &              prune &   $40$ &   $0.424$ &   $0.845$ \\
% 10 &              prune &   $60$ &   $0.425$ &   $0.815$ \\
% 11 &  diff prune global &   $99$ &   $0.230$ &   $0.901$ \\
% 12 &  diff prune global &   $99$ &   $0.222$ &   $0.905$ \\
% 13 &         diff prune &   $99$ &   $0.222$ &   $0.913$ \\
% 14 &         diff prune &   $95$ &   $0.221$ &   $0.916$ \\
% 15 &         diff prune &   $90$ &   $0.216$ &   $0.916$ \\
% 16 &         diff prune &   $60$ &   $0.209$ &   $0.920$ \\
% 17 &                rank reduction &  $100$ &   $0.515$ &   $0.823$ \\
% 18 &                rank reduction &  $150$ &   $0.456$ &   $0.828$ \\
% 19 &         diff prune &   $80$ &   $2.533$ &   $0.491$ \\
% 20 &         diff prune &   $90$ &       --- &       --- \\
% 21 &  diff prune global &    $0$ &   $0.738$ &   $0.509$ \\
% 22 &         diff prune &    $0$ &   $0.692$ &   $0.522$ \\
% 23 &         diff prune &    $0$ &   $1.854$ &   $0.491$ \\
% \bottomrule
% \end{tabular}

@@

\begin{figure*}[htb]
\centering
\includegraphics[width=\textwidth]{../figs/kd_lstm_training.png}
\caption{Training loss (left), val. loss (middle), and val. accuracy
(right) plotted against number of batches of training for LSTM KD}
\label{fig:kdlstmloss}
\end{figure*}

Our most striking result is the robust performance of difference pruning. Even
keeping upwards of 99\% of the weights unchanged gives us performance that is
very competitive with the unrestricted model. Most of our experiments are on
SST-2, but we see success with this method on QQP as well, suggesting that
small changes to pretrained BERT are sufficient for performance on a specific
task.

As expected, difference pruning a higher proportion of the weights decreases
performance, but we are happily surprised at the relatively low magnitude of
this effect even at high prune rates. Pruning with a global threshold rather
than in a stratified way produces distinctly worse results. We suspect this is
due to weights in different layers having different magnitudes, making a global
threshold have an undue effect on layers whose weights tend to be smaller. We
confirm this heterogeneity in \cref{fig:weightsbylayer}.

@@

Our non-difference distortions are more sensitive to the compression parameter
(whether prune rate or rank reduction rank). We find it difficult to achieve performance
comparable to the uncompressed BERT with a significantly compressed model. Among
the different distortion methods, we favor pruning for its computational
simplicity, and see no evidence that rank reduction achieves better compression.

Remarkably, the fact that pruning and rank reduction incurs significant
losses to the
model seems to show that popular compression techniques that enjoy success
in convolutional neural networks fail to generalize good performance to
transformer-based language networks like BERT. We present some preliminary
evidence in \Cref{fig:singular-values}, where we plot the singular values
in one of the matrices in BERT. The effective rank of the matrix seems
quite high, as the singular values are all sizable, decaying at a rate too
slow for rank reduction techniques to be promising. This suggests that
matrices in BERT are in fact effectively dense, unlike CNNs, where
good compression relies on the effective sparsity of the matrices. 
\begin{figure}[tb]
    \centering
    \includegraphics[width=0.5\textwidth]
    {../figs/svd-singular-vals-distribution.png}
    \caption{Distribution of singular values in one of BERT layers}
    \label{fig:singular-values}
\end{figure}

@@

@@

Knowledge Distillation displayed promise by improving student networks'
performance versus training only on the classes $y_i$. However, the student
networks fell short of replicating uncompressed BERT's performance. It is
possible that future variations on our work could achieve competitive
compression. In particular, we restrict our knowledge distillation only to the
samples in the original training set. However, there is no need to perform
training so narrowly since the teacher network can annotate any unsupervised
data. It is likely that doing so would further increase performance, though we
can only speculate as to the magnitude of the benefit.

It is also possible that our choice of student network colored our results. We
aimed for architectures known to work on SST-2 while being much smaller, such as
\citet{kim2014convolutional}'s CNN. It is possible that we aimed too small and
would be better served by a more complex model---possibly even a smaller version
of BERT. Finally, in all our experiments our teacher network is a single
fine-tuned version of BERT. Since teacher network complexity doesn't contribute
to the complexity of the final model, we could instead use an ensemble of BERTs
(or even other models) as our teacher network.

The DeepTwist framework---particularly when combined with difference
pruning---exceeded our expectations for compression. It would be interesting to
test whether this generalizes to a wider array of tasks, particularly since we
only reap compression benefits as we leverage weight sharing over a number of
tasks. Furthermore, from the distortions presented in \citet{lee2018deeptwist},
we did not implement clustering-based quantization because of the significant
computational bottleneck clustering with $k$-means on all of BERT's parameters
posed. Future work could attempt to surmount this obstacle whether through
increased computational resources or a more scalable clustering algorithm.

Finally, we recognize our approaches are but a subset of the ways to go about
compressing large language models such as BERT. Two alternatives stand out as
particularly exciting possible future directions. \citet{liu2019multi} propose a
method for complete weight sharing of BERT's encoder parameters across different
tasks by simultaneously training for all tasks. We believe this approach could
be relaxed through difference pruning to achieve a performance gain relative to
each compression technique in isolation.

\citet{frankle2018lottery} articulate in their ``lottery ticket hypothesis''
that most networks contain sparse sub-networks which can perform similarly well.
They provide an algorithm for finding these ``lottery tickets'' whose main
differences to DeepTwist are (1) that weights that get distorted to 0 are permanently
masked and kept at 0, and (2) that the algorithm progressively increases the
pruning rate. This framework could serve as a competitive alternative to
DeepTwist, and it would be interesting to see how it performs with difference
pruning.

\section*{Acknowledgements}

We thank Alexander M. Rush and the Harvard CS 287 community, without whom
this work would not have been possible.

% TODO: thank Rush + 287

>>>>

\begin{abstract}
\raggedright
  \begin{itemize}
  \item We apply model compression techniques to fine-tuned BERT on multiclass
  classification problems.
  \item Knowledge distillation and DeepTwist-based compression techniques give
  us moderate compression benefits for a commensurate decrease in model
  performance.
  \item We achieve our most compelling results from employing the DeepTwist
  framework to share weights across BERT models fine-tuned for different tasks.
  \item Our work demonstrates most weights need not change in the fine-tuning
  process.
%   \item This document describes the expected style, structure, and rough
%   proportions for your final project write-up.
%   \item While you are free to break from this structure, consider it a strong
%   prior for our expectations of the final report.
%   \item Length is a hard constraint. You are only allowed max \textbf{8 pages}
%   in this format. While you can include supplementary material, it will not be
%   factored into the grading process. It is your responsibility to convey the
%   main contributions of the work in the length given.
  \end{itemize}

@@

Deep Neural Networks (DDNs) have become the state-of-art for many tasks in
language modeling. At the same time, they have become progressively larger in
size, due to both larger out-of-box pre-trained embeddings and deeper
networks. However, in order to deploy the models on more resource-constrained
devices, such as mobile devices or even older personal laptops, as opposed to
on cloud virtual machines, it is crucial to reduce the size of the models.

@@

In this paper, we demonstrate that the DeepTwist framework
\citep{lee2018deeptwist} is applicable to compressing fine-tuned BERT
\citep{devlin2018bert} on multiclass classification problems in addition to
computer vision tasks, though the drop in performance is less negligible.
Knowledge Distillation also achieves the compression objective with more than
desired decrease in predictive accuracy.

@@

The most important contribution of this paper is that we proposed a new
weight-sharing method called ``Difference Pruning'' which imposes constraint on
the sparcity of weight difference with the pre-trained BERT model. While
uncompressed fine-tuned BERT model achieves 92.9\% validation accuracy on
SST-2, the Difference Pruning model that keeps 99\% of the pre-trained BERT
weights achieves 91.3\% on the validation set. This enables multiple language
modeling tasks to share the weights of pre-trained BERT and each incurs minimal
extra storage space requirements.

@@

DNNs have become extremely large in size with growing complexities. A BERT
base model has 110M parameters and takes 438 MB disk space to store. This
makes it very hard to deploy those models on mobile devices, which in most
cases have limited storage and RAM and low computational resources. As a
result, we are not able to store multiple models for different tasks on mobile
devices. Allocating hundreds of megabytes to to those models is also not
realistic for mobile apps such as Gmail or Facebook. And due to increasing
privacy concerns, users prefer models generating predictions based on their
input to be running locally instead of sending information to the cloud. Last
but not least, evaluating enormous models takes too much time on mobile
devices and can drain batteries significantly.

The challenge that we are facing is therefore how to compress DNNs in size
while keeping their predictive performance competitive with full model.

@@

We are interested in compressing the language representation model BERT
\citep{devlin2018bert}.  It is the state-of-art result in many natural
language processing tasks  such as natural language inference, paraphrasing
and named entity recognition.

\citet{cheng2017survey} provides a comprehensive overview of the state-of-art
methods to compress DNNs. Of the methods summarized by the paper, the ones
that are of interest to our work are weight-pruning and quantization
\citep{han2015deep}, and low-rank factorization \citep{denton2014exploiting}.
Knowledge distillation, first proposed by \citep{bucilua2006model} as
``knowledge transfer'', was recently popularized by
\citep{hinton2015distilling}. It differs from the previously mentioned methods
since it compresses an existing model by replacing it with a simpler model
that is trained on its outputs.

DeepTwist, a end-to-end training framework, allows us to incorporate
compression procedures into training \citep{lee2018deeptwist}. Under this
framework, the model parameters are occasionally distorted during training
time instead of only at the end. This framework has the benefit of simplified
training procedure and faster convergence and reduced requirement for
hyperparameter tuning. Experiment on MNIST dataset with DeepTwist shows that
LeNet-5 and LeNet-300-100 models are able to retain predictive accuracy under
high compression rate.

@@

An additional benefit from knowledge distillation arises from BERT's
pre-training. Because BERT is pre-trained on large amounts of unstructured
data, it contains a powerful language model which likely would be impossible
to learn from the specific task's data-set. To an extent, relevant features
from this language model are what make BERT so powerful once it's fine-tuned.
Training the student network on BERT's output thus allows some of this
``outside knowledge'' to percolate toward the student network.

@@

\subsection{Deep Twist}

@@

We list a few methods of parameterizing the distortion step. 
\paragraphdot{Pruning} Consider a parameter vector $\bvartheta$, let
  $t_p$ be the $p$-th quantile of the vector $\bvartheta$. Then \[
  \prune(\bvartheta; p) = \one(|\bvartheta| > t_p) \odot \bvartheta
  \]
  be the vector where values in $\bvartheta$ below $t_p$ are zeroed.

@@

  Pruning is an out-of-the-box procedure that works with any models. However,
  as a price of the generality, pruning fails to be tailored to the nature of
  BERT being a pre-trained model. Suppose the pretrained weights $\bphi_0 $
  capture certain structure of language, then dramatic distortions to
  $\bphi_0$ essentially discards the information, especially early in the
  training loop. We may partially remedy this issue by either using a dynamic
  pruning rate, where pruning rate is small early in the training loop or by
  using layer-specific pruning rates, with layers in $\bert$ having a lower
  pruning rate than layers in $G$.

@@

We distort via \[
\rankreduce(\bvartheta; r) = \tilde U \tilde \Sigma \tilde V^\top,
\]
where $\tilde U, \tilde \Sigma, \tilde V$ are conforming matrices such that the
smallest values on the spectrum $\Sigma$ is zeroed out, as well as corresponding
values in $U,V$. If we keep only the $r$ largest spectral values, then we store
$\tilde U \tilde \Sigma$, an $n\times r$ matrix, and $\tilde V$, an $m\times r$
matrix. Thus, instead of storing $2nm$ floats, we may store $r(n+m)$, achieving
a compression rate of \[
\rho = \frac{r(n+m)}{2mn}.
\]
Note however, that storing matrices in this manner requires an additional
matrix multiplication in evaluation time, since we have to compute the product
$\tilde U \tilde \Sigma \tilde V$.

% \subsection{Knowledge Distillation}

% Example Structure:

% \begin{itemize}
% \item What is the formal definition of your problem?
% \item What is the precise mathematical model you are using to represent it? In
% almost all cases this will use the probabilistic language from class, e.g.
%   \begin{equation}
%   z \sim {\cal N}(0, \sigma^2)\label{eq:1}
% \end{equation}
% But it may also be a neural network, or a non-probabilistic loss,
% \[ h_t \gets \mathrm{RNN}(x_{t}, h_{t-1} )\]

% This is also a good place to reference a diagram such as Figure~\ref{fig:diagram}.

% \item What are the parameters or latent variables of this model that you plan
% on estimating or inferring? Be explicit. How many are there? Which are you
% assuming are given? How do these relate to the original problem description?
% \end{itemize}

% \begin{figure}
%   \centering
%   \missingfigure[figheight=8cm]{}
%   \caption{\label{fig:diagram} This is a good place to include a diagram
%   showing how your model works. Examples include a graphical model or a neural
%   network block diagram.}
% \end{figure}

% \subsection{Knowledge Distillation}

% Example Structure:

% \begin{itemize}
% \item What is the formal definition of your problem?
% \item What is the precise mathematical model you are using to represent it? In
% almost all cases this will use the probabilistic language from class, e.g.
%   \begin{equation}
%   z \sim {\cal N}(0, \sigma^2)\label{eq:1}
% \end{equation}
% But it may also be a neural network, or a non-probabilistic loss,
% \[ h_t \gets \mathrm{RNN}(x_{t}, h_{t-1} )\]

% This is also a good place to reference a diagram such as Figure~\ref{fig:diagram}.

% \item What are the parameters or latent variables of this model that you plan
% on estimating or inferring? Be explicit. How many are there? Which are you
% assuming are given? How do these relate to the original problem description?
% \end{itemize}

% \begin{figure}
%   \centering
%   \missingfigure[figheight=8cm]{}
%   \caption{\label{fig:diagram} This is a good place to include a diagram
%   showing how your model works. Examples include a graphical model or a neural
%   network block diagram.}
% \end{figure}

\section{Methods}
In this section, we briefly discuss our experimental setup. We mostly
work with
SST-2, a binary sentiment classification task in the GLUE multitask benchmark
framework \citep{wang2018glue}. We also validate the model's
performance with trial on the Quora Question Pair (QQP) task, which is a
binary classification task for whether two questions are equivalent. We
train with a maximum sequence length of 64 and batch size of 32 on the
NC-6 and NC-12 virtual machines on Microsoft Azure. We use the basic 
\texttt{BERT-base-uncased} model for our experimental results. We employ
early stopping in training, with patience of 1 epoch, and early stopping is
guided by validation error.

@@

For knowledge distillation experiments, we use various configurations of the
student network: \paragraphdot{LSTM} We use a one-layer LSTM network with hidden
dimension $H=200$. We first embed the one-hot representation of tokens, and we
feed the embeddings through an LSTM. We then map the last hidden state of the
LSTM through a linear layer for classification.  \paragraphdot{CNN} We use an
implementation\footnote{\url{https://github.com/jfilter/cnn-text-classification-pytorch/blob/master/cnn_text_classification/model.py}}
of \citet{kim2014convolutional} with kernel sizes $(3,4,5)$, hidden size
$H=300$, no dropout, and $20$ kernels for each kernel size.\footnote{These are
default in the implementation we used.}

@@

\begin{itemize}
\item What were the results comparing previous work / baseline systems / your
systems on the main task?
\item What were the secondary results comparing the variants of your system?
\item This section should be fact based and relatively dry. What happened, what
was significant?
\end{itemize}

@@

% \begin{table}[tbh]
%         \caption{Results for DeepTwist}
%         \label{tab:deeptwist_results}
%         \centering
%         \vspace{1em}
%         \begin{tabular}{lccccc}
% \toprule
% {} &               type &  param &  val loss &   val acc \\
% {} & 
% \hypertarget{tabcol:1}{(1)} & \hypertarget{tabcol:2}{(2)} & \hypertarget{tabcol:3}{(3)} & \hypertarget{tabcol:4}{(4)} \\ \midrule
% 0  &  diff prune global &   $90$ &   $0.211$ &   $0.912$ \\
% 1  &              prune &   $20$ &   $0.291$ &   $0.886$ \\
% 2  &              prune &   $80$ &   $0.532$ &   $0.767$ \\
% 3  &         diff prune &   $80$ &   $0.222$ &   $0.916$ \\
% 4  &  diff prune global &   $99$ &       --- &       --- \\
% 5  &  diff prune global &   $90$ &   $0.213$ &   $0.916$ \\
% 6  &         diff prune &   $40$ &   $0.203$ &   $0.909$ \\
% 7  &                svd &   $50$ &   $0.490$ &   $0.810$ \\
% 8  &                svd &  $200$ &   $0.459$ &   $0.845$ \\
% 9  &              prune &   $40$ &   $0.424$ &   $0.845$ \\
% 10 &              prune &   $60$ &   $0.425$ &   $0.815$ \\
% 11 &  diff prune global &   $99$ &   $0.230$ &   $0.901$ \\
% 12 &  diff prune global &   $99$ &   $0.222$ &   $0.905$ \\
% 13 &         diff prune &   $99$ &   $0.222$ &   $0.913$ \\
% 14 &         diff prune &   $95$ &   $0.221$ &   $0.916$ \\
% 15 &         diff prune &   $90$ &   $0.216$ &   $0.916$ \\
% 16 &         diff prune &   $60$ &   $0.209$ &   $0.920$ \\
% 17 &                svd &  $100$ &   $0.515$ &   $0.823$ \\
% 18 &                svd &  $150$ &   $0.456$ &   $0.828$ \\
% 19 &         diff prune &   $80$ &   $2.533$ &   $0.491$ \\
% 20 &         diff prune &   $90$ &       --- &       --- \\
% 21 &  diff prune global &    $0$ &   $0.738$ &   $0.509$ \\
% 22 &         diff prune &    $0$ &   $0.692$ &   $0.522$ \\
% 23 &         diff prune &    $0$ &   $1.854$ &   $0.491$ \\
% \bottomrule
% \end{tabular}

@@

Our most striking result is the robust performance of difference pruning. Even
keeping upwards of 99\% of the weights unchanged gives us performance that is
very competitive with the unrestricted model. Most of our experiments are on
SST-2, but we see success with this method on QQP as well, suggesting that
small changes to pre-trained BERT are sufficient for performance on a specific
task.

As expected, pruning a higher proportion of the weights decreases performance,
but we are happily surprised at the relatively low magnitude of this effect even
at high prune rates. Pruning with a global threshold rather than in a
stratified way produces distinctly worse results. We suspect this is due to
weights in different layers having different magnitudes, making a global
threshold have an undue effect on layers whose weights tend to be smaller. We
confirm this heterogeneity in \cref{fig:weightsbylayer}.

@@

Our non-difference distortions are more sensitive to the compression parameter
(whether prune rate or SVD rank). We find it difficult to achieve performance
comparable to the uncompressed BERT with a significantly compressed model. Among
the different distortion methods, we favor pruning for its computational
simplicity, and see no evidence that SVD achieves better compression.

@@

\begin{figure*}[tb]
\centering
\includegraphics[width=\textwidth]{../figs/kd_lstm_training.png}
\caption{Training loss (left), val. loss (middle), and val. accuracy
(right) for LSTM KD}
\label{fig:kdlstmloss}
\end{figure*}

@@

\begin{itemize}
\item What happened?
\item What next?
\end{itemize}

% \section*{Acknowledgements}
